Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-09-10 drafts/outline.tex
overleaf

Many previous studies on sediment capture through vegetated reaches have used laboratory flume experiments to examine the effects of different flow and vegetation conditions on the rate and efficiency of sediment removal from the water column (\cite{Fauria_2015, Palmer_2004, Purich_2007,  Zhang_reconfiguration_2020, Zhang_turbulence_2020}). Laboratory flume experiments are valuable because interaction between vegetation and flow can produce complex mixing patterns and turbulence structures that require experiments to validate and describe hypotheses and theory (\cite{Nepf_2012, Nepf_2008}). Sediment capture is defined as as one of the mechanisms by which sediment is removed from suspended load by vegetation stems, also referred to as collectors; Capture efficiency is defined as the efficiency of collectors in removing sediment particles from suspension in water.

Might need some more exposition about different quantities considered and basic definitions (ex. sediment capture, what a collector is, efficiency, etc)

@@

Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps, which were spaced uniformly throughout the test section in order to estimate the mass of sediment settled due to gravity. Each trap consisted of a hollow plastic cylinder with a small perforated disk affixed to the inside, on which was placed a glass microfiber filter paper to capture sediment. Nine sediment traps were used, configured in a shape approximating a $3 \times 3$ grid (Figure \ref{fig:floorplan}).

>>>>

Many previous studies on sediment capture through vegetated reaches have used laboratory flume experiments to examine the effects of different flow and vegetation conditions on the rate and efficiency of sediment removal from the water column (\cite{Fauria_2015, Palmer_2004, Purich_2007,  Zhang_reconfiguration_2020, Zhang_turbulence_2020}). Laboratory flume experiments are valuable because interaction between vegetation and flow can produce complex mixing patterns and turbulence structures that require experiments to validate and describe hypotheses and theory (\cite{Nepf_2012, Nepf_2008}). Sediment capture is defined as as one of the mechanisms by which sediment is removed from suspended load by vegetation stems, also referred to as collectors; capture efficiency is defined as the efficiency of collectors in removing sediment particles from suspension in water (need references on these definitions).

@@

Holes measuring approximately 2.5 cm in diameter were drilled in the array to hold the sediment traps. Each trap consisted of a hollow plastic cylinder with a small perforated disk affixed to the inside, on which was placed a glass microfiber filter paper to capture sediment. Nine traps were used, which were distributed throughout the test section with the goal of capturing longitudinal and lateral differences in settling should they occur (Figure \ref{fig:floorplan}).
